---
title: "2-15-23 Practice Lors"
author: "Seth Lors"
date: "2023-02-15"
output: html_document
---

Initial Setup
```{r}
library(classdata)
head(fbiwide)
ggplot2::ggplot()
```

1. Draw a scatter plot of the log transformed number of burglaries by motor vehicle thefts. Map the state variable to colour. Why is this a terrible idea?
This is a bad idea because there are too many states to make the difference between some states distinct enough. For example, Alaska, and Arizona have similar      colors but different values.
```{r}
ggplot(data = fbiwide, aes(x = log(burglary), y = log(motor_vehicle_theft))) + geom_point(aes(color = state))
```
Question 2
Draw a scatterplot of the log transformed number of burglaries by motor vehicle thefts. Map population to size. How do we interpret the output?
```{r}
ggplot(data = fbiwide, aes(x = log(burglary), y = log(motor_vehicle_theft))) + geom_point(aes(color = state, size = population))
```
Question 3
Draw a scatterplot of the log transformed number of burglaries by motor vehicle thefts. Map Population to size. How do we interpret the output?
```{r}
ggplot(data = fbiwide[fbiwide$year == 2019, ], aes(x = population)) + geom_histogram()
```
Question 4
Compare the log transformed number of burglaries by motor vehicle thefts over years. How to make a nice plot?
```{r}
fbiwide1 = fbiwide
fbiwide1 = fbiwide1[fbiwide1$year >= 1980, ]
fbiwide1 = fbiwide1[fbiwide1$year < 2020, ]
fbiwide1$decade = floor(fbiwide1$year / 10)
fbiwide1$decade = paste0(fbiwide1$decade, "0s")

ggplot(data = fbiwide1, aes(x = log(burglary), y = log(motor_vehicle_theft))) + geom_point(aes(color = decade))
```
Question 5
Compare the log transformed number of burglaries by motor vehicle thefts over States, coloured by years.
```{r}
ggplot(data = fbiwide1, aes(x = log(burglary), y = log(motor_vehicle_theft))) + geom_point(aes(color = decade)) + facet_wrap(.~ state_abbr)
```
Question 6
Now, only focus on comparing California, Colorado, Iowa, Illinois, District of Columbia and New York.
```{r}
state.subset = c("California", "Colorado", "Iowa", "Illinois", "District of Columbia", "New York")

fbiwide2 = fbiwide1[fbiwide1$state %in% state.subset, ]
ggplot(data = fbiwide2, aes(x = log(burglary), y = log(motor_vehicle_theft))) + geom_point(aes(color = decade)) + facet_wrap(.~ state)
```
Question 7
We all know population is an important factor. How to compare different states by standardized population?
```{r}
ggplot(data = fbiwide2, aes(x = log(burglary / population * 66424), y = log(motor_vehicle_theft / population * 66424))) + geom_point(aes(color = decade)) + facet_wrap(.~ state)
```

```
